\section{Introduction}
The development of complex software intensive systems involves interactions between different subsystems. For instance, embedded and cyber-physical systems require the interaction of multiple computing resources (general-purpose processors, DSP, GPU), and various digital or analog devices (sensors, actuators) connected through a wide range of heterogeneous communication resources (buses, networks, meshes).

To deal with complexity issues in the development of applications for complex systems, Model Driven Engineering (MDE) proposes to rely on \emph{Models}. A model is an abstraction of the real word made in order to facilitate an understanding of the way it works. In the context of MDE, a software model enables a developer to reduce the complexity of an application by ignoring non-essential details. In this sense, The Object Management Group (OMG) defines that \emph{a model is a representation of a part of the function, structure and/or behavior of a system. The model specification is based on a language that has a well-defined form (syntax), meaning (semantics) and possible rules of analysis, inferences or proof for its constructs”}. This enables the developer to reason about the application. To built models, MDE proposes \emph{Domain Specific Modeling Languages} (DSMLs). They are built by an expert to describe the structure but also the behavior of a domain. As a result, a DSML, as any other language, is defined by a syntax and a behavioral semantics. 

The development of complex applications may involve several DSMLs. Each expert uses its own language to describe its domain. This results in a heterogeneous specification, \ie made of models that conform to different DSMLs. Furthermore, nowadays systems are more and more coupled. As a result, system designers need to get a global representation to reason about the system as a whole. For instance, a system designer must be able to perform verification and validation activities of the overall system. To get a global representation, system designer needs to combine models in a structural and behavioral way. In this thesis, we use the word \emph{composition} to refer to the combination of structural models/languages to obtain a new structural model/language. Conversely, we use the word \emph{coordination} to refer the specification of the interactions between the behaviors of models/language into a new model so-called \emph{Model of Coordination}.   
 
In this chapter, we first present an overview of composition approaches. They propose to compose the structure of models/languages to obtain a new model/language. Afterwards, we present state-of-the-art approaches that coordinate the behavior of languages/models. In these latter approaches, the interactions between languages/models are specified as a new model. By relying on these approaches, we conclude this chapter with the requirements for our language \bcool.        
